Title here

### 2016-09-21 portfolio/text/ms.Rmd

Title should emphasize individuals, e.g. "Benefits of diversification and risks of changing strategies for individual fishermen/fishers"
<!-- Fishing is inherently risky and we have long-sought regulations and fishing behaviors that reduce this risk. -->
<!-- The increasing the diversity of species fished has been proposed to reduce risk for fishermen -->

@@

Despite this existing work,
key questions remain on the relationship between diversty of fish catches and
fishing revenue variability.
First, the effect of changing species diversity
for individual permit holders on a year-by-year basis is unknown ---
existing approaches have worked at the vessel or community level
and condensed time series into single metrics of variability or risk.
Second, the effect of changing species diversity
on revenue itself is unknown ---
existing approaches have focused solely on variability or risk.
Third, it is unknown if the approach to
diversifying species fished affects the relationship between
species diversity and revenue variability ---
a fisheries permit holder can purchase
an additional permit to target other species,
pick a permit that inherently targets many species,
or increase species diversity
within the constraints of his or her existing permits.
Many permit holders may be limited to the last approach
given that the first two may be costly and limited by regulations,
but it is unclear if the benefits and costs are the same.
Here, we address these questions by
simultaneously estimating the effects of
these three approaches to species diversification
for Alaskan fishery permit holders on
annual revenue and revenue variability.

I think we need a little here on the AK data and why that's both important and generalizable to fisheries around the world. 
Fisheries in Alaska are the highest valued fisheries in N. America
with landings valued at XX $ billion annually. There are a number of fishing
strategies where both specialization and diversification are extremely profitable. There's a number of fishing permits that constrain the potential diversity of species landed (e.g. herring, halibut, sablefish, or crab permits that allow the user to only land that species) versus broader 'finfish' permits that allow users to land a wide variety of groundfish spp. 
- perhaps we also need to have a sentence or two on the implict constraints of geography and gear / vessel size on species diversification

Our model makes use of the entire time series,
controls for effort and latent time effects,
and allows the effect of species diversity
to vary by fishing strategy (sets of similar permits)
in a hierarchical model.

<!-- Multiple ways one can diversify: -->
<!-- buy another permit, pick diverse permit, diversify within existing constraints. -->

@@

Our models focused on species diversity
as a possible predictor of revenue and revenue variability
while controlling for effort.
We calculated effective species diversity for
permit holder $i$ and time (year) $t$ as the inverse of
Simpson's diversity index (Jost 2006; also referred to in economics as the Herfindahl-Hirschman Index) $\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity') (also say we did this for consistency with previous analyses,e.g. Kasperski and Holland):

@@

The general framework of our model is known as a variance function regression model, which separately models change in the mean and variance as a function of covariates (Davidian and Carrol 1987 http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1987.10478543; Hall and Carrol 1989, http://www.jstor.org/stable/2345837; ). Where traditional linear models or hierarchical linear models generally assume constant variance, the variance function regression model allows variance to be heteroscedastic. For application to economic data on individual fishing portfolios, this type of model allows certain strategies and levels of diversification to be more or less variable than others.

@@

The $\beta$'s represent estimated coefficients, some of which are allowed to vary as random effect terms.
The intercepts $\beta_{0,j,t}$ are allowed to vary by
strategy-year combinations,
are centered on zero, and are constrained by a normal distribution:

@@

EW: part of the difference is individuals vs vessels. For example, K&H suggested that diversity declined following IFQs for halibut sablefish vessels. The reason for the decline was that the vessels were allowed to fish halibut for more days (because people were sharing boats). At the level of people, we wouldn't expect the diversity of someone who only had halibut/sablefish permit to be affected by IFQs. The person, not the vessel holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq

- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification (unless you have a M or salmon permit)
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person

>>>>

*Eric: Title should emphasize individuals, e.g. "Benefits of diversification and risks of changing strategies for individual fishermen/fishers"*
<!-- Fishing is inherently risky and we have long-sought regulations and fishing behaviors that reduce this risk. -->
<!-- The increasing the diversity of species fished has been proposed to reduce risk for fishermen -->

@@

Despite this existing work,
key questions remain on the relationship between 
diversity of fish catches and
fishing revenue variability.
First, the effect of changing species diversity
for individual permit holders on a year-by-year basis is unknown ---
existing approaches have worked at the vessel [@kasperski2013],
fleet [@sethi2012b], or community level [@sethi2014],
and condensed time series into single metrics of variability or risk.
Second, the effect of changing species diversity
on revenue itself is unknown ---
existing approaches have focused solely on variability or risk.
Third, it is unknown if the approach to
diversifying species fished affects the relationship between
species diversity and revenue variability ---
a fishery permit holder can purchase
an additional permit to target other species,
pick a permit that inherently targets many species,
or increase species diversity
within the constraints of his or her existing permits.
Many permit holders may be limited to the last approach
given that the first two may be costly and limited by regulations,
but it is unclear if the benefits and costs are the same.
Here, we address these questions by
simultaneously estimating the effects of
these three approaches to species diversification
for Alaskan fishery permit holders on
annual revenue and revenue variability.
Our model makes use of entire time series,
controls for effort and latent time effects,
and allows the effect of species diversity
to vary by fishing strategy (sets of similar permits)
in a hierarchical model.

*Eric: I think we need a little here on the AK data and why that's both important and generalizable to fisheries around the world. 
Fisheries in Alaska are the highest valued fisheries in N. America
with landings valued at XX $ billion annually. There are a number of fishing
strategies where both specialization and diversification are extremely profitable. There's a number of fishing permits that constrain the potential diversity of species landed (e.g. herring, halibut, sablefish, or crab permits that allow the user to only land that species) versus broader 'finfish' permits that allow users to land a wide variety of groundfish spp. 
- perhaps we also need to have a sentence or two on the implicit constraints of geography and gear / vessel size on species diversification*

@@

Our models focused on species diversity
as a possible predictor of revenue and revenue variability
while controlling for effort.
We calculated effective species diversity for
permit holder $i$ and time (year) $t$ as the inverse of
Simpson's diversity index 
(TODO - Jost 2006; also referred to in economics as the Herfindahl-Hirschman Index) 
$\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity') 
*Eric: (also say we did this for consistency with previous analyses,e.g. Kasperski and Holland):*

@@

The general framework of our model is known as a variance function
regression model, which separately models change in the mean and variance as
a function of covariates (TODO - Davidian and Carrol 1987
http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1987.10478543; Hall
and Carrol 1989, http://www.jstor.org/stable/2345837). Where traditional
linear models or hierarchical linear models generally assume constant
variance, the variance function regression model allows variance to be
heteroskedastic. For application to economic data on individual fishing
portfolios, this type of model allows certain strategies and levels of
diversification to be more or less variable than others.

@@

The $\beta$'s represent estimated coefficients, some of which are allowed to
vary as 'random effect' terms.
The intercepts $\beta_{0,j,t}$ are allowed to vary by
strategy-year combinations,
are centered on zero, and are constrained by a normal distribution:

@@

- EW: part of the difference is individuals vs vessels. For example, K&H
suggested that diversity declined following IFQs for halibut sablefish
vessels. The reason for the decline was that the vessels were allowed to
fish halibut for more days (because people were sharing boats). At the level
of people, we wouldn't expect the diversity of someone who only had
halibut/sablefish permit to be affected by IFQs. The person, not the vessel
holds the quota share: https://alaskafisheries.noaa.gov/fisheries/ifq
- Year to year risky... But maybe evens out/better over time
- diversity within permit - often bycatch, limited room for intentional diversification (unless you have a M or salmon permit)
- Risk results not really risk, but unpredictability given our covariates ...
don't change anything and it's most predictable how well you'll do
- What's unpredictable in our model, might be more predictable on a year to
year, species by species basis for individual permit holder
- Equilibrium, average variability vs year to year effect for one person
